---
title: "Assigment - kNN DIY"
author:
  - Chihiro Ono - Author
  - Lotte Ulrich - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

------------------------------------------------------------------------

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train your own kNN model. Follow all the steps from the CRISP-DM model.

## Business Understanding

Columns from 4 to 13 indicates the component of blood. So, I'll make a knn that classify the category of people based on components.

## Data Understanding

Read the url from Github

```{r}
url<- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-Chihirono/master/datasets/KNN-hcvdat0.csv"
rawDF<- read.csv(url)

str(rawDF)
```

## Data Preparation

I delete the first raw because it is not necessary.

```{r}
cleanDF <- rawDF[-1]
View(cleanDF)

cntCategory <- table(cleanDF$Category)
propCategory <- round(prop.table(cntCategory) * 100 , digits = 1)

cntCategory
```

```{r}
cleanDF$Category <- factor(cleanDF$Category, levels = c("0=Blood Donor", "0s=suspect Blood Donor","1=Hepatitis","2=Fibrosis","3=Cirrhosis"), labels = c("Blood Donor","suspect Blood Donor","Hepatitis","Fibrosis", "")) 
View(cleanDF) 

```

```{r}
cleanDF[is.na(cleanDF)]<-0
```

```{r}
summary(cleanDF[c("ALB","ALP","ALT","AST","BIL","CHE","CHOL","CREA","GGT","PROT")])
```

Check the quality of function for normalization

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet2))
```

apply this function to the real data set These lines did not work.

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(4:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()


summary(cleanDF_n[c("ALB","ALP","ALT","AST","BIL","CHE","CHOL","CREA","GGT","PROT")])
```

I changed the same name of the columns that rstudio somehow named. It works, but I cannot use it later because of the name.

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(3:nCols, function(){normalize(cleanDF[,x])}) %>% as.data.frame(
View(cleanDF_n)
summary(cleanDF_n[c("V1","V2","V3",,"V5","V6","V7","V8","V9","V10")])
```

```{r}
trainDF_feat <- cleanDF_n[1:515,1  ]
testDF_feat <- cleanDF_n[516:615,1  ]
```

```{r}
trainDF_labels <- cleanDF[1:515,  1]
testDF_labels <- cleanDF[516:615,  1]
```

## Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_test_pred)
```

## Evaluation and Deployment

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

reviewer adds suggestions for improving the model

## line 54
Wrong line:
```{r}
cleanDF$Category <- factor(cleanDF$Category, levels = c("0=Blood Donor", "0s=suspect Blood Donor","1=Hepatitis","2=Fibrosis","3=Cirrhosis"), labels = c("Blood Donor","suspect Blood Donor","Hepatitis","Fibrosis", "")) 
```
Needs to be:
```{r}
cleanDF$Category <- factor(cleanDF$Category, levels = c("0=Blood Donor", "0s=suspect Blood Donor","1=Hepatitis","2=Fibrosis","3=Cirrhosis"), labels = c("Blood Donor","suspect Blood Donor","Hepatitis","Fibrosis","Cirrhosis"))
```
-> misses "Cirrhosis" in labels = c()

## line 100
Wrong line:
```{r}
cleanDF_n <- sapply(3:nCols, function(){normalize(cleanDF[,x])}) %>% as.data.frame(
```
Needs to be:
```{r}
cleanDF_n <- sapply(4:nCols, function(x){normalize(cleanDF[,x])}) %>% as.data.frame
```
-> misses x in function() and sapply(3:nCols, needs to be sapply(4:nCols

## line 102
Wrong line:
```{r}
summary(cleanDF_n[c("V1","V2","V3",,"V5","V6","V7","V8","V9","V10")])
```
Needs to be:
```{r}
summary(cleanDF_n[c("V1","V2","V3","V4","V5","V6","V7","V8","V9","V10")])
```
-> misses "V4" in cleanDF_n[c()]

## line 125
Wrong line:
```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```
Needs to be:
```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels, positive = NULL, dnn = c("Prediction", "True"))
```
-> [[1]] needs to be removed. The [[1]] makes the names uneven and that's why it can't run.
